\textbf{\supplement}\vskip 2ex \mytitle\vskip 2ex

### 2023-05-27 paper-seb-supplementary-material.tex
Lots of simplifications to using multiple Latex files

\def\href#1{#1}

@@

% pageref gives us a hyperlink which looks unsightly, so we do it this way...
\makeatletter

@@

\makeatletter
\def\globalLabel#1{% we also need journal code-policies to be used in the main paper...
\typeout{Global globalLabel: #1}%
\immediate\write\infofileForMain{\bslash newlabel{#1}{{\arabic{section}}{\thepage}{DUMMYA}{DUMMYB}{DUMMYC}}}
% as well as in the current document....
\immediate\write\@auxout{\bslash newlabel{#1}{{\bslash arabic{section}\dotalph{subsection}}{\thepage}{AAA}{BBB}{CCC}}}
}
\def\globalTableLabel#1{% we also need journal code-policies to be used in the main paper...
\typeout{Global globalTableLabel: #1}%
\immediate\write\infofileForMain{\bslash newlabel{#1}{{\arabic{table}}{\thepage}{DUMMYA}{DUMMYB}{DUMMYC}}}
% as well as in the current document....
\immediate\write\@auxout{\bslash newlabel{#1}{{\bslash arabic{table}\dotalph{subsection}}{\thepage}{AAA}{BBB}{CCC}}}
}
\def\globalLabelValue#1#2{% we also need journal code-policies to be used in the main paper...
\typeout{Global globalLabelValue: #1 := #2}%
\immediate\write\infofileForMain{\bslash newlabel{#1}{{#2}{\thepage}{AAA}{BBB}{CCC}}}
}
\makeatother

@@

\section{Software engineering best practice}
\label{supplementary-best-practice}
%\subsection{Introduction and standard references}

@@

\subsection{Usability}
\globalLabel{supplementary-material-makefiles}
Usability is an important consideration: \cite{hci1,hci2} is the program usable by its intended users so they can obtain correct results? Often the programmers developing code know it so well they misjudge how easy it will be for anyone else to use it --- this is a very serious problem for the lone programmer (possibly working in another country) supporting a research team. Usability is especially important when programs are to be used by other researchers and by non-programmers, including epidemiologists.

@@

\section{Code, data, and publication}
\globalLabel{on-code-data-publication}

@@

More of such techniques for improving reliability are discussed in section \ref{data-methods-subsection}, where they are applied to accurately and reliably reporting the survey reported in the main paper.

@@

\subsection{Comparing conventional and RAP approaches}
\globalLabel{RAP-diagrams}
The similarities and differences between the conventional copy-and-paste approach to filling in data and diagrams in publications, the improved systematic RAP process, and using notebooks (such as \emph{Mathematica\/} or Jupyter), are illustrated in the sequence of schematics of figures \ref{fig:basic}, \ref{fig:excel}, \ref{fig:rap}, and \ref{fig:notebook}.

\begin{figure} 
   \centering
   \includegraphics[width=5in]{generated/basic.\imageFileSuffix} 
   \caption{The common basic --- error-prone and obsolete --- approach to scientific authoring is to use code to help generate analyses and diagrams, then manually copy and paste the selected results into the publication. Note that the publication, including the results, can be edited arbitrarily, and typically the results published will have been edited and modified (if only for typographical purposes) from those actually generated by the code.}
   \label{fig:basic}
\end{figure}
\begin{figure} 
   \centering
   \includegraphics[width=5in]{generated/excel.\imageFileSuffix} 
   \caption{When the code is in a spreadsheet, such as Microsoft Excel, the code is generally hidden from sight. The data copied \& pasted into a publication may or may not be calculated from data in other cells (such as column totals). Records are rarely taken of these manual processes, and, anyway, typically it is impossible to be certain exactly what has been copied unless very great care is taken. In consequence, if a spreadsheet is modified, it is haphazard what results are updated and corrected in the publication. }
   \globalLabelValue{excelFigure}{\thefigure}
   \label{fig:excel}
\end{figure}
\begin{figure} 
   \centering
   \includegraphics[width=5in]{generated/import.\imageFileSuffix} 
   \caption{Improving over the normal approach (figure \ref{fig:basic}), data and diagrams are placed in the publication using a programmed, systematic approach. In the present paper, this was done by generating text files of \LaTeX\ definitions (represented by boxes in the central column of the schematic), hence providing \LaTeX\ names for all of the code-generated values. Since the copying of results into a publication is automated and easy, any improvements to the results (such as correcting errors) are made by improving the code --- which therefore contributes to improving all future-generated results too. Not shown, but in well-engineered code, documentation will also be generated, such as by using tools such as JavaDoc or Doxygen.}
   \label{fig:rap}
\end{figure}
\begin{figure}[t]
   \centering
   \includegraphics[width=5in]{generated/notebook.\imageFileSuffix} 
   \caption{In a notebook system, such as \emph{Mathematica\/} or Jupyter, a single document --- the notebook --- integrates the publication, the code, any notes, as well as all the results. The code generates results and images that are automatically (and reliably) inserted in place into the notebook, usually right after the code that generates them. Some parts of the notebook are marked or selected to be printed as the publication, thus allowing most if not all code to be hidden from the final publication. In well-engineered code, the notebook will directly contain full documentation.
Note that in most systems, notebooks can import and generate arbitrary data (images, sounds, sensor data, etc).}
   \label{fig:notebook}
\end{figure}

\section{The Spiegelhalter trustworthiness questions}
\globalLabel{supplementary-Spiegelhalter-section}

@@

\sequestion{How rigorously has the Software Engineering been done? Section \ref{supplementary-best-practice} in the \supplement\ provides a list of important issues that must be addressed for any reliable software.}

@@

\sequestion{How are the claims presented that give us confidence in the code that they are based on? Are there discussions of invariants, independent checks for errors, and so on? Again, \supplement\ section \ref{supplementary-best-practice} provides further discussion of such issues.}

@@

\sequestion{These are all good statistical questions. The Software Engineering analogy is: are the claims backed up by a sufficiently detailed discussion of the algorithms and Software Engineering that justify the appropriateness of the chosen software implementation? The \supplement\ list in section \ref{supplementary-best-practice} provides examples of expected explanations for the trustworthiness of running some code.}

@@

\section{A pilot survey of computational science}
\globalLabel{survey-section}

@@

%There are many ways to do good science. Normal science routinely involves either performing new research and reporting it in the literature, or performing reviews --- such as systematic reviews --- of the existing literature to form a consensus view of an existing body of research. Typically, research offers new theories or results, points out previous errors, or uses statistical or qualitative methods to reduce the variability in previously reported results. In any case, the intention is to provide reliable knowledge and to bolster consensus \cite{ziman}.

@@

Moreover, this paper itself follows the more general \RAPstar\ methodology. For example, as standard practice, a Unix makefile is used to make it easy to analyze and generate all data, typeset the paper, and more. Table \ref{table:options} shows the options provided.

\begin{table}[t]
\begin{center}
\input generated/make-help.tex
\end{center}
\caption{Conforming to the \RAPstar\ methodology, the abbreviated summary above was generated automatically, by using \texttt{make data}. A full list of \texttt{make} options is generated by \texttt{make} or \texttt{make help} when run on the Unix command line. %(Saying \texttt{make help} would generate a full summary on the command line.)
}
\label{table:options}
\end{table}

@@

\subsubsection{\emph{Journal of Vascular Surgery}}\label{vascular-surgery-note}
In 2020 the \emph{Journal of Vascular Surgery\/} published a research paper \cite{jvs1}, which had to be retracted on ethical grounds \cite{jvs2,jvs3}: it was a na\"\i ve study and the editorial process was unaware of digital norms. Notably, the paper fails to provide access to its anonymized data (with or without qualification), and fails to define the data anonymization algorithm, and also fails to even mention the code that it developed and used to perform its study. The journal's data policy is itself very weak (the authors ``should consider'' including a footnote to offer limited access to the data) and, despite basic statistics policies, it has no policy at all for code (see  section \ref{supplementary-journal-policies-section}). Ironically, the retracted article \cite{jvs1} is still online (as of August 2020) with no reference to any editorial statement to the effect that it has been retracted, despite this being trivial --- and necessary --- to achieve in the widely-accessed online medium.

@@

\caption{Sizes of repositories, with approximate sizes of code (in kLOC) and data for all available GitHub repositories reviewed in the survey, plus \texttt{covid-sim} \cite{ICmodel} for comparison. Sizes are approximate because in all repositories code and data are conceptually interchangeable (an issue explained in the \supplement), so choices were made in the survey to avoid double-counting. Many repositories rely on downloading additional code and data, which is not counted in the table as the additional required material is not in the repository cited in the paper.  At the time of cloning and checking all repositories in \clonewhen, paper \csname cite-PostoperativeOutcomes.RiskNet\endcsname\ still had nothing in its repository except a single file still saying ``\ldots\ code coming soon~\ldots,'' despite \the\pubdelayinmonths\ months having already elapsed since the  paper had claimed the code could be accessed in its repository.}
\label{table-repo-summary}\globalTableLabel{supplementaryTableRepoSummary}
\end{table*}

@@

\item the code/data policies of the \plural{\numberOfJournals}{journal} condoned at the time of the sample \emph{and continue to condone\/} poor practice at the time of writing the present paper (\monthname{\month} \the\year) --- for specific details and further explanation of the problems, see \supplement\ section \ref{supplementary-journal-policies-section};

@@

\subsection{Summary of results}
\label{summary-of-results}
The sample selection criteria necessarily identified scientific research with Software Engineering contributions.

@@

There was no evidence of any critical assessment of code, suggesting that scientists writing papers take it for granted that their code works as they intend. No competent programmer would take it for granted that their code was correct without following rigorous methods, such as formal methods, regression testing, test driven design, etc (see section \ref{supplementary-best-practice} in this \supplement).

@@

With the one minor exception, no papers reported anything on any Software Engineering methodologies, which is astonishing given the scale of some of the software effort supporting the papers (table \ref{table-repo-summary}).  The papers themselves, typically only a few published pages, are very brief compared to the substantial code they rely on (see table \ref{table-repo-summary}).

@@

\emph{Nature Digital Medicine\/} and \emph{Royal Society Open Science\/} have clear data and code policies (see \supplement\ section \ref{supplementary-journal-policies-section}), but actual publishing practice falls short: \the\countHasBreach\ out of the \plural{\countHasPolicy}{paper} (\pc{\countHasBreach}{\countHasPolicy}) published in them and sampled in the survey manifestly breach their code policies. In contrast, \emph{Lancet Digital Health\/}, despite substantial data policies, has no code policy at all to breach. The implication is that the fields, and the editorial expertise of leading journals, misunderstand and dismiss code policies --- they (or their editors and reviewers) are technically unable to assess them. This lack of expertise is consistent with the limited awareness of Software Engineering best practice that is manifest in the published papers (and resources) themselves.

Code repositories were used by \plural{\countUsesVersionControlRepository}{paper} (\pc{\countUsesVersionControlRepository}{\dataN}), though \plural{\countNoCodeInRepo}{paper} in the survey claimed to have code on GitHub but there was no code in the repository, only the comment ``Code coming soon\ldots'' (checked at the time of doing the review, then double-checked as detailed in the references in the \supplement, as well as most recently on \clonedate\
while checking table \ref{table-repo-summary}): in other words, the repository had never been used and the code could never have been looked at, let alone reviewed.\footnote{GitHub records show that it had not been deleted after paper submission.} This is a pity because GitHub provides help and targeted warnings and hints like ``No description, website, or topics provided [\ldots] no releases published.'' The lack of code is ironic: the paper concerned \csname cite-PostoperativeOutcomes.RiskNet\endcsname\ has as its title ``\emph{Development and validation\/} of a deep neural network model [\ldots]'' (our emphasis), yet it provides no code or development processes for the runnable model it claims to validate, so nobody else (including referees) can check any of the paper's specific claims.

The sizes of all GitHub repositories are summarized in table \ref{table-repo-summary} (since many papers not using GitHub do not have all code available, non-GitHub code sizes are not easily compared and are not listed).

@@

\subsubsection{Current code policies of sampled journals}
\globalLabel{supplementary-journal-policies-section}

It is noteworthy that none of the journals sampled permit any reliable style of managing data in published papers, such as described above in sections \ref{detecting-against-error} and \ref{restrictive-policies}. The main paper, section \ref{mentionPLOSandIEEE}, additionally mentions \emph{PLOS ONE\/} and \emph{IEEE Transactions on Software Engineering}.

@@

\noindent\textbf{Extract from \emph{Royal Society Open Science\/} author guidelines} \\ 
{\sf``It is a condition of publication that authors make the primary data, materials (such as statistical tools, protocols, software) and code publicly available. These must be provided at the point of submission for our Editors and reviewers for peer-review, and then made publicly available at acceptance. [\ldots] As a minimum, sufficient information and data are required to allow others to replicate all study findings reported in the article. Data and code should be deposited in a form that will allow maximum reuse. As part of our open data policy, we ask that data and code are hosted in a public, recognized repository, with an open licence (CC0 or CC-BY) clearly visible on the landing page of your dataset.''}\specifyurl\url{royalsociety.org/journals/authors/author-guidelines/#data}\specifyaccess{Since first accessed 29 July 2020, the policy has been revised (undated, accessed 2 February 2022) but retains the same principles; full policy now available via a DOI \cite{RS-policy}. The policy still retains an emphasis on data accessibility, and continues a lack of awareness that code and data are equivalent and often mixed (see section \ref{on-code-data-publication}).}

@@

\noindent\textbf{Extract from \emph{Journal of Vascular Surgery\/} author guidelines}\\
The \emph{Journal of Vascular Surgery\/} has detailed data policies, but no code policy. While no \emph{Journal of Vascular Surgery\/} papers were surveyed (but see section \ref{vascular-surgery-note}), the following statement on data policies is relevant:

@@

{
\def\citenum#1{\cite{#1}}
\begin{longtable}{@{}cp{2.8in}p{2.8in}@{}}
\sf\bfseries Ref&\sf\bfseries Data&\sf\bfseries Code \\ \hline \endhead 
\input generated/assessments.tex
\end{longtable}
}

\label{data-methods-section}
\subsection{Assessment criteria and methods}
\label{data-methods-subsection}
A survey sampled of recent papers that were published online in July 2020, accepted for publication after peer review in \the\numberOfJournals\ high-profile, highly competitive leading peer-reviewed journals, namely \journalBreakdown. Papers were selected from the journals' July 2020 new online listings where the paper's title implied that code had been used in the research. Commentary, correspondence and editorials were excluded. The sample represents what the editorial and the broader peer review community considers to be good practice.

@@

Some of the files generated from the JSON data are Unix shell scripts. For example, details of all the papers with GitHub repositories are automatically collected into a shell script so the repositories can be cloned locally and then measured (as it happens, using \texttt{awk} scripts), e.g., to generate table \ref{table-repo-summary} for this \supplement.

@@

\subsubsection{Detecting and defending against error}
\label{detecting-against-error}
% check it works for other numbers 
%\countUsesVersionControlRepository=296

@@

\subsubsection{Problems of restrictive journal policies}
\globalLabel{restrictive-policies}
Automatically generated variables are used throughout the paper and this \supplement.
As usual, \LaTeX\ detects any spelling errors in the use of variables, thus helping protect the paper against typos that could otherwise mislead the paper's readers. Conveniently, \LaTeX\ also supports sophisticated calculations itself \cite{latex-calculus}, so the typeset paper can use any variable values in further calculations without going back to modify the data source file (in the present case, \texttt{data.js}). In practice this enables the author to avoid copying-and-pasting values from a data source or calculator, and then overlooking keeping them up to date with changes to the data or formula required.

For example, the caption of table \ref{table-repo-summary} in the main paper calculates its ``\plural{\pubdelayinmonths}{month}'' figure from the generated variables recording the repository date of cloning used to provide the data to construct the table. The number of months will of course be correctly updated if the paper's repository \csname cite-PostoperativeOutcomes.RiskNet\endcsname\ is subsequently checked again:

@@

\input generated/supplementary-references.tex

>>>>

% pageref gives us a hyperlink which looks unsightly, so we do it this way...
\def\href#1{#1}

@@

\makeatletter

@@

%\makeatletter
%\def\globalLabel#1{% we also need journal code-policies to be used in the main paper...
%\typeout{Global globalLabel: #1}%
%\immediate\write\infofileForMain{\bslash newlabel{#1}{{\arabic{section}}{\thepage}{DUMMYA}{DUMMYB}{DUMMYC}}}
%% as well as in the current document....
%\immediate\write\@auxout{\bslash newlabel{#1}{{\bslash arabic{section}\dotalph{subsection}}{\thepage}{AAA}{BBB}{CCC}}}
%}
%\def\globalTableLabel#1{% we also need journal code-policies to be used in the main paper...
%\typeout{Global globalTableLabel: #1}%
%\immediate\write\infofileForMain{\bslash newlabel{#1}{{\arabic{table}}{\thepage}{DUMMYA}{DUMMYB}{DUMMYC}}}
%% as well as in the current document....
%\immediate\write\@auxout{\bslash newlabel{#1}{{\bslash arabic{table}\dotalph{subsection}}{\thepage}{AAA}{BBB}{CCC}}}
%}
%\def\globalLabelValue#1#2{% we also need journal code-policies to be used in the main paper...
%\typeout{Global globalLabelValue: #1 := #2}%
%\immediate\write\infofileForMain{\bslash newlabel{#1}{{#2}{\thepage}{AAA}{BBB}{CCC}}}
%}
%\makeatother

@@

\section{Software engineering best practice}
\label{supplement-best-practice}

@@

\subsection{Usability}
\label{supplement-material-makefiles}
Usability is an important consideration: \cite{hci1,hci2} is the program usable by its intended users so they can obtain correct results? Often the programmers developing code know it so well they misjudge how easy it will be for anyone else to use it --- this is a very serious problem for the lone programmer (possibly working in another country) supporting a research team. Usability is especially important when programs are to be used by other researchers and by non-programmers, including epidemiologists.

@@

\section{Code, data, and publication}
\label{supplement-on-code-data-publication}

@@

More of such techniques for improving reliability are discussed in section \ref{supplement-data-methods-subsection}, where they are applied to accurately and reliably reporting the survey reported in the main paper.

@@

\subsection{Comparing conventional and RAP approaches}
\label{supplement-RAP-diagrams}
The similarities and differences between the conventional copy-and-paste approach to filling in data and diagrams in publications, the improved systematic RAP process, and using notebooks (such as \emph{Mathematica\/} or Jupyter), are illustrated in the sequence of schematics of figures \ref{supplement-fig:basic}, \ref{supplement-fig:excel}, \ref{supplement-fig:rap}, and \ref{supplement-fig:notebook}.

\begin{figure} 
   \centering
   \includegraphics[width=5in]{generated/basic.\imageFileSuffix} 
   \caption{The common basic --- error-prone and obsolete --- approach to scientific authoring is to use code to help generate analyses and diagrams, then manually copy and paste the selected results into the publication. Note that the publication, including the results, can be edited arbitrarily, and typically the results published will have been edited and modified (if only for typographical purposes) from those actually generated by the code.}
   \label{supplement-fig:basic}
\end{figure}
\begin{figure} 
   \centering
   \includegraphics[width=5in]{generated/excel.\imageFileSuffix} 
   \caption{When the code is in a spreadsheet, such as Microsoft Excel, the code is generally hidden from sight. The data copied \& pasted into a publication may or may not be calculated from data in other cells (such as column totals). Records are rarely taken of these manual processes, and, anyway, typically it is impossible to be certain exactly what has been copied unless very great care is taken. In consequence, if a spreadsheet is modified, it is haphazard what results are updated and corrected in the publication. }
   \label{supplement-fig:excel}
\end{figure}
\begin{figure} 
   \centering
   \includegraphics[width=5in]{generated/import.\imageFileSuffix} 
   \caption{Improving over the normal approach (figure \ref{supplement-fig:basic}), data and diagrams are placed in the publication using a programmed, systematic approach. In the present paper, this was done by generating text files of \LaTeX\ definitions (represented by boxes in the central column of the schematic), hence providing \LaTeX\ names for all of the code-generated values. Since the copying of results into a publication is automated and easy, any improvements to the results (such as correcting errors) are made by improving the code --- which therefore contributes to improving all future-generated results too. Not shown, but in well-engineered code, documentation will also be generated, such as by using tools such as JavaDoc or Doxygen.}
   \label{supplement-fig:rap}
\end{figure}
\begin{figure}[t]
   \centering
   \includegraphics[width=5in]{generated/notebook.\imageFileSuffix} 
   \caption{In a notebook system, such as \emph{Mathematica\/} or Jupyter, a single document --- the notebook --- integrates the publication, the code, any notes, as well as all the results. The code generates results and images that are automatically (and reliably) inserted in place into the notebook, usually right after the code that generates them. Some parts of the notebook are marked or selected to be printed as the publication, thus allowing most if not all code to be hidden from the final publication. In well-engineered code, the notebook will directly contain full documentation.
Note that in most systems, notebooks can import and generate arbitrary data (images, sounds, sensor data, etc).}
   \label{supplement-fig:notebook}
\end{figure}

\section{The Spiegelhalter trustworthiness questions}
\label{supplement-Spiegelhalter-section}

@@

\sequestion{How rigorously has the Software Engineering been done? Section \ref{supplement-best-practice} in the \supplement\ provides a list of important issues that must be addressed for any reliable software.}

@@

\sequestion{How are the claims presented that give us confidence in the code that they are based on? Are there discussions of invariants, independent checks for errors, and so on? Again, \supplement\ section \ref{supplement-best-practice} provides further discussion of such issues.}

@@

\sequestion{These are all good statistical questions. The Software Engineering analogy is: are the claims backed up by a sufficiently detailed discussion of the algorithms and Software Engineering that justify the appropriateness of the chosen software implementation? The \supplement\ list in section \ref{supplement-best-practice} provides examples of expected explanations for the trustworthiness of running some code.}

@@

\section{A pilot survey of computational science}
\label{supplement-survey-section}

@@

%There are many ways to do good science. Normal science routinely involves either performing new research and reporting it in the literature, or performing reviews --- such as systematic reviews --- of the existing literature to form a consensus view of an existing body of research. Typically, research offers new theories or results, points out previous errors, or uses statistical or qualitative methods to reduce the variability in previously reported results. In any case, the intention is to provide reliable knowledge and to bolster consensus \xcite{ziman}.

@@

Moreover, this paper itself follows the more general \RAPstar\ methodology. For example, as standard practice, a Unix makefile is used to make it easy to analyze and generate all data, typeset the paper, and more. Table \ref{supplement-table:options} shows the options provided.

\begin{table}[t]
\begin{center}
\input generated/make-help.tex
\end{center}
\caption{Conforming to the \RAPstar\ methodology, the abbreviated summary above was generated automatically, by using \texttt{make data}. A full list of \texttt{make} options is generated by \texttt{make} or \texttt{make help} when run on the Unix command line. %(Saying \texttt{make help} would generate a full summary on the command line.)
}
\label{supplement-table:options}
\end{table}

@@

\subsubsection{\emph{Journal of Vascular Surgery}}\label{supplement-vascular-surgery-note}
In 2020 the \emph{Journal of Vascular Surgery\/} published a research paper \cite{jvs1}, which had to be retracted on ethical grounds \cite{jvs2,jvs3}: it was a na\"\i ve study and the editorial process was unaware of digital norms. Notably, the paper fails to provide access to its anonymized data (with or without qualification), and fails to define the data anonymization algorithm, and also fails to even mention the code that it developed and used to perform its study. The journal's data policy is itself very weak (the authors ``should consider'' including a footnote to offer limited access to the data) and, despite basic statistics policies, it has no policy at all for code (see section \ref{supplement-journal-policies-section}). Ironically, the retracted article \cite{jvs1} is still online (as of August 2020) with no reference to any editorial statement to the effect that it has been retracted, despite this being trivial --- and necessary --- to achieve in the widely-accessed online medium.

@@

\caption{Sizes of repositories, with approximate sizes of code (in kLOC) and data for all available GitHub repositories reviewed in the survey, plus \texttt{covid-sim} \cite{ICmodel} for comparison. Sizes are approximate because in all repositories code and data are conceptually interchangeable (an issue explained in the \supplement), so choices were made in the survey to avoid double-counting. Many repositories rely on downloading additional code and data, which is not counted in the table as the additional required material is not in the repository cited in the paper.  At the time of cloning and checking all repositories in \clonewhen, paper \csname cite-PostoperativeOutcomes.RiskNet\endcsname\ still had nothing in its repository except a single file still saying ``\ldots\ code coming soon~\ldots,'' despite \the\pubdelayinmonths\ months having already elapsed since the  paper had claimed the code could be accessed in its repository.}
\label{supplement-table-repo-summary}
\end{table*}

@@

\item the code/data policies of the \plural{\numberOfJournals}{journal} condoned at the time of the sample \emph{and continue to condone\/} poor practice at the time of writing the present paper (\monthname{\month} \the\year) --- for specific details and further explanation of the problems, see \supplement\ section \ref{supplement-journal-policies-section};

@@

\subsection{Summary of results}
\label{supplement-summary-of-results}
The sample selection criteria necessarily identified scientific research with Software Engineering contributions.

@@

There was no evidence of any critical assessment of code, suggesting that scientists writing papers take it for granted that their code works as they intend. No competent programmer would take it for granted that their code was correct without following rigorous methods, such as formal methods, regression testing, test driven design, etc (see section \ref{supplement-best-practice} in this \supplement).

@@

With the one minor exception, no papers reported anything on any Software Engineering methodologies, which is astonishing given the scale of some of the software effort supporting the papers (table \ref{supplement-table-repo-summary}).  The papers themselves, typically only a few published pages, are very brief compared to the substantial code they rely on (see table \ref{supplement-table-repo-summary}).

@@

\emph{Nature Digital Medicine\/} and \emph{Royal Society Open Science\/} have clear data and code policies (see \supplement\ section \ref{supplement-journal-policies-section}), but actual publishing practice falls short: \the\countHasBreach\ out of the \plural{\countHasPolicy}{paper} (\pc{\countHasBreach}{\countHasPolicy}) published in them and sampled in the survey manifestly breach their code policies. In contrast, \emph{Lancet Digital Health\/}, despite substantial data policies, has no code policy at all to breach. The implication is that the fields, and the editorial expertise of leading journals, misunderstand and dismiss code policies --- they (or their editors and reviewers) are technically unable to assess them. This lack of expertise is consistent with the limited awareness of Software Engineering best practice that is manifest in the published papers (and resources) themselves.

Code repositories were used by \plural{\countUsesVersionControlRepository}{paper} (\pc{\countUsesVersionControlRepository}{\dataN}), though \plural{\countNoCodeInRepo}{paper} in the survey claimed to have code on GitHub but there was no code in the repository, only the comment ``Code coming soon\ldots'' (checked at the time of doing the review, then double-checked as detailed in the references in the \supplement, as well as most recently on \clonedate\
while checking table \ref{supplement-table-repo-summary}): in other words, the repository had never been used and the code could never have been looked at, let alone reviewed.\footnote{GitHub records show that it had not been deleted after paper submission.} This is a pity because GitHub provides help and targeted warnings and hints like ``No description, website, or topics provided [\ldots] no releases published.'' The lack of code is ironic: the paper concerned \csname cite-PostoperativeOutcomes.RiskNet\endcsname\ has as its title ``\emph{Development and validation\/} of a deep neural network model [\ldots]'' (our emphasis), yet it provides no code or development processes for the runnable model it claims to validate, so nobody else (including referees) can check any of the paper's specific claims.

The sizes of all GitHub repositories are summarized in table \ref{supplement-table-repo-summary} (since many papers not using GitHub do not have all code available, non-GitHub code sizes are not easily compared and are not listed).

@@

\subsubsection{Current code policies of sampled journals}
\label{supplement-journal-policies-section}

It is noteworthy that none of the journals sampled permit any reliable style of managing data in published papers, such as described above in sections \ref{supplement-detecting-against-error} and \ref{supplement-restrictive-policies}. The main paper, section \ref{mentionPLOSandIEEE}, additionally mentions \emph{PLOS ONE\/} and \emph{IEEE Transactions on Software Engineering}.

@@

\noindent\textbf{Extract from \emph{Royal Society Open Science\/} author guidelines} \\ 
{\sf``It is a condition of publication that authors make the primary data, materials (such as statistical tools, protocols, software) and code publicly available. These must be provided at the point of submission for our Editors and reviewers for peer-review, and then made publicly available at acceptance. [\ldots] As a minimum, sufficient information and data are required to allow others to replicate all study findings reported in the article. Data and code should be deposited in a form that will allow maximum reuse. As part of our open data policy, we ask that data and code are hosted in a public, recognized repository, with an open licence (CC0 or CC-BY) clearly visible on the landing page of your dataset.''}\specifyurl\url{royalsociety.org/journals/authors/author-guidelines/#data}\specifyaccess{Since first accessed 29 July 2020, the policy has been revised (undated, accessed 2 February 2022) but retains the same principles; full policy now available via a DOI \cite{RS-policy}. The policy still retains an emphasis on data accessibility, and continues a lack of awareness that code and data are equivalent and often mixed (see section \ref{supplement-on-code-data-publication}).}

@@

\noindent\textbf{Extract from \emph{Journal of Vascular Surgery\/} author guidelines}\\
The \emph{Journal of Vascular Surgery\/} has detailed data policies, but no code policy. While no \emph{Journal of Vascular Surgery\/} papers were surveyed (but see section \ref{supplement-vascular-surgery-note}), the following statement on data policies is relevant:

@@

{
\begin{longtable}{@{}cp{2.8in}p{2.8in}@{}}
\sf\bfseries Ref&\sf\bfseries Data&\sf\bfseries Code \\ \hline \endhead 
\input generated/assessments.tex
\end{longtable}
}

\subsection{Assessment criteria and methods}
\label{supplement-data-methods-subsection}
A survey sampled of recent papers that were published online in July 2020, accepted for publication after peer review in \the\numberOfJournals\ high-profile, highly competitive leading peer-reviewed journals, namely \journalBreakdown. Papers were selected from the journals' July 2020 new online listings where the paper's title implied that code had been used in the research. Commentary, correspondence and editorials were excluded. The sample represents what the editorial and the broader peer review community considers to be good practice.

@@

Some of the files generated from the JSON data are Unix shell scripts. For example, details of all the papers with GitHub repositories are automatically collected into a shell script so the repositories can be cloned locally and then measured (as it happens, using \texttt{awk} scripts), e.g., to generate table \ref{supplement-table-repo-summary} for this \supplement.

@@

\subsubsection{Detecting and defending against error}
\label{supplement-detecting-against-error}
% check it works for other numbers 
%\countUsesVersionControlRepository=296

@@

\subsubsection{Problems of restrictive journal policies}
\label{supplement-restrictive-policies}
Automatically generated variables are used throughout the paper and this \supplement.
As usual, \LaTeX\ detects any spelling errors in the use of variables, thus helping protect the paper against typos that could otherwise mislead the paper's readers. Conveniently, \LaTeX\ also supports sophisticated calculations itself \cite{latex-calculus}, so the typeset paper can use any variable values in further calculations without going back to modify the data source file (in the present case, \texttt{data.js}). In practice this enables the author to avoid copying-and-pasting values from a data source or calculator, and then overlooking keeping them up to date with changes to the data or formula required.

For example, the caption of table \ref{supplement-table-repo-summary} in the main paper calculates its ``\plural{\pubdelayinmonths}{month}'' figure from the generated variables recording the repository date of cloning used to provide the data to construct the table. The number of months will of course be correctly updated if the paper's repository \csname cite-PostoperativeOutcomes.RiskNet\endcsname\ is subsequently checked again:

@@

\input generated/supplementary-references.bbl
